---
title: "ROAR-CAT: cat simulation"
author: "Wanjing Anya Ma"
date:  "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
---

# Load packages

```{r, message=FALSE, warning = FALSE, echo = FALSE}
library("knitr") # for rendering the RMarkdown file
library("tidyverse") # for data wrangling 
library(dplyr)
library(mirt)
library('ggpubr')
library(ggplot2)
library("catR")
library(reshape)
library(Metrics)
library(corrplot)
library(rstudioapi)
library(patchwork)
library(viridis)
```

# Settings

```{r echo = FALSE}
# sets how code looks in knitted document
opts_chunk$set(comment = "")

# suppresses warning about grouping 
options(dplyr.summarise.inform = F)
```

# mirt Model
```{r}
mirt0.2 <- load("../models/mirt_model_0.2.rda")

mirt0.3 <- load("../models/mirt_model_0.3.rda")

mirt0.2.order <- load("../models/resp_order_theta_brs_model_0.2.rda")
```

# Data

## Data Loading
```{r warning = FALSE, message = FALSE}
df.data <- read_csv("../data/school/roar_swr_rp_grouped_anonymized.csv") 

df.data.rt <-  read_csv("../data/school/roar_swr_rp_grouped_anonymized_rt.csv")
```

validation data
```{r}
df.student <- read_csv( "../data/school/swr_validation_study_trials_with_guessing.csv")
```

## remove guessing participants 

```{r}
df.data.rt.transformed <- df.student %>% 
  mutate(rt = ifelse(rt == 0, 0.01, rt)) %>% 
  mutate(log_rt = log(rt)) %>% 
  group_by(pid, runId, variant, block) %>% 
  summarise(median_log_rt = median(log_rt), median_rt = median(rt), pc = mean(correct)) 

mean_value <- mean(df.data.rt.transformed$median_log_rt)
sd_value <- sd(df.data.rt.transformed$median_log_rt)

threshold <- mean_value - 3*sd_value

print(threshold)

df.student.v2 <- df.data.rt.transformed %>% 
  filter(median_log_rt >= threshold) %>%
  ungroup() %>% 
  left_join(df.student, by = c("pid", "runId", "variant", "block"))
```
additional filter

We keep particiapnts who doesn't have any block has median response time lower than 2 standard deviation
```{r}
df.included.names <- df.student.v2 %>% 
  group_by(pid, runId,  variant) %>% 
  tally() %>% 
  filter(n == 246) 
```

```{r}
df.student.final <- df.student.v2 %>% 
  filter(runId %in% df.included.names$runId)
```

```{r}
df.excluded.participants <- df.student %>% 
  filter(!pid %in% df.included.names$pid) %>% 
  group_by(variant, pid, block) %>% 
  mutate(block = as.character(block + 1)) %>% 
  summarise(pc = mean(correct), 
            median_rt = median(rt), 
            median_log_rt = median(log(rt))) %>% 
  mutate(guessing = ifelse(median_log_rt < threshold, TRUE, FALSE)) 

ggplot(df.excluded.participants, mapping = aes(x = block,
                     y = median_rt)) +
  geom_point(alpha=.6, aes(color = guessing)) +
  facet_wrap(~variant) + 
  geom_line(aes(group=pid), alpha=.4) + 
  scale_color_manual(values=c( "black", "darkred")) + 
  labs(x = "block number",
       y = "median response time per item (ms)",
       title = "rapid-guessing particiapnts")
  
```

## Descriptive Summary
```{r}
df.student.summary <- df.student.final %>% 
  filter(trialNumTotal == 246) %>% 
  dplyr ::select(pid, variant, ageMonths, trueEstimate = thetaEstimate) %>% 
  left_join(df.student.final %>% 
  group_by(variant, pid) %>% 
  summarise(median_rt = median(log(rt))))

df.student.summary %>% 
  group_by(variant) %>% 
  summarise(n = n(), 
            mean(ageMonths), sd(ageMonths), mean(trueEstimate), sd(trueEstimate), mean(median_rt), sd(median_rt))
```

```{r}
t_test_result_ability <- t.test(trueEstimate ~ variant, data = df.student.summary)

t_test_result_ability
```
```{r}
t_test_result_age <- t.test(ageMonths ~ variant, data = df.student.summary)

t_test_result_age
```
```{r}
t_test_result_rt <- t.test(median_rt ~ variant, data = df.student.summary)

t_test_result_rt
```
## Visualize the distributions

```{r}
df.student.summary.long <- df.student.summary %>% 
  mutate(variant = ifelse(variant == "adaptive", "ROAR-CAT", "ROAR-Random")) %>% 
  dplyr :: select(-ageMonths) %>% 
  dplyr :: rename(`theta estimate` = trueEstimate, `median response time in log scale (ms)` = median_rt) %>% 
  pivot_longer(cols = c(`theta estimate`, `median response time in log scale (ms)`), names_to = "metrics")

```

```{r fig.width=10,fig.height=5}
ggplot(df.student.summary.long, aes(value, linetype = variant)) + 
  geom_density(size=1) + 
  facet_wrap(~metrics, scales = "free", switch = "x") +
  theme(legend.text = element_text(size = 15),
        strip.text = element_text(size = 15),
        legend.title = element_blank(),
        axis.text= element_text(size=15),
        axis.title = element_text(size=15),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        strip.placement = "outside",
        strip.background = element_blank()) 

ggsave("../plots/roar_cat_study2_figure1.png")
ggsave("../plots/roar_cat_study2_figure1.pdf")
```

## Visualize three participants with different levels
```{r}
fisherInfo <- function(th, a, b, c){
  p = c + (1-c) * exp(a*(th - b))/(1+ exp(a*(th - b)))
  q = 1- p 
  return  ((a^2) * (q/p) * ((p-c)^2) / ((1-c)^2))
  
}
```
```{r}
df.student.selected.trueTheta <- df.student.final %>% 
  filter(trialNumTotal == 246, variant == "adaptive") %>% 
  filter(pid %in% c('v-C9uf0s-837', "v-feUpZD-904", "v-woMyqy-876")) %>%
  select(pid, thetaEstimate) %>% 
  mutate(trueTheta = thetaEstimate) %>% 
  select(pid, trueTheta)
  
```
```{r}
df.student_longer <- df.student.final %>% 
  filter(pid %in%  c('v-C9uf0s-837', "v-feUpZD-904", "v-woMyqy-876")) %>% 
  dplyr::rename(`item difficulty` = difficulty, `theta estimate` = thetaEstimate) %>% 
  pivot_longer(cols = c(`item difficulty` , `theta estimate`)) %>% 
  mutate(correct = as.character(correct))
```

```{r echo = FALSE}

ggplot(df.student_longer %>% dplyr :: rename(`item type` = realpseudo), mapping = aes(x = trialNumTotal,
                     y = value, 
                     color = name, 
                     shape = `item type`)) +
  facet_wrap(~pid, labeller = labeller(pid = c("v-feUpZD-904" = "middle performer", 'v-woMyqy-876' = "high performer",'v-C9uf0s-837' = "low performer"))) +
  ylim(-6, 6) +
  labs(x = "Number of items",
       y = "Item difficulty or theta estimate") +
  theme(legend.position = "bottom", 
        legend.title = element_blank()) +
  scale_color_manual(values=c("#8F993E", "#E05A1D")) +
  geom_point(size = 1) 

ggsave("../plots/roar_cat_study2_SI_1.png")
ggsave("../plots/roar_cat_study2_SI_1.pdf")
```

## Sanity check: checking item information for the first 10 items between variants
```{r}
df.student.selected.trueTheta <- df.student.final %>% 
  filter(trialNumTotal == 246) %>% 
  #filter(pid %in% c('v-C9uf0s-837', "v-feUpZD-904", "v-woMyqy-876")) %>%
  dplyr :: select(pid, thetaEstimate) %>% 
  mutate(trueTheta = thetaEstimate) %>% 
  dplyr ::select(pid, trueTheta)

df.student.information.top10.items <- df.student.final %>% 
  dplyr::rename(`item difficulty` = difficulty, `theta estimate` = thetaEstimate) %>% 
  left_join(df.student.selected.trueTheta) %>% 
  mutate(itemInformation = fisherInfo(`theta estimate`, 1, `item difficulty`, 0.5)) %>% 
  arrange(pid, trialNumTotal) %>%
  filter(trialNumTotal <= 10) %>% 
  group_by(variant, trialNumTotal) %>%
  dplyr :: summarise(sd_itemInformation = sd(itemInformation),mean_itemInformation = mean(itemInformation),count = n()) %>% 
  mutate(variant = ifelse(variant == "adaptive", "ROAR-CAT", "ROAR-Random"))

ggplot(df.student.information.top10.items, aes(x = trialNumTotal, y = mean_itemInformation, color = variant)) +
  geom_point(position = position_dodge(width = 0.2), size = 2) +
  geom_errorbar(aes(ymin = mean_itemInformation - sd_itemInformation, ymax = mean_itemInformation + sd_itemInformation),
                width = 0.2, position = position_dodge(width = 0.2)) +
   scale_x_continuous(breaks = seq(1, 10, by = 1), labels = seq(1, 10, by = 1)) +
  labs(title = "Item information of the selected item (mean and standard deviation)",
       x = "Number of test items",
       y = "Item information of the selected item",
       color = "Variant") 
```

# Item Bank for Cat Simulation
```{r}
df.word_params_new <- read_csv("../corpus/item_bank_v3.csv")
```
```{r}
plot.test.information <- function (items) {
  # Define the probability function for the 4PL model
prob_1pl <- function(theta, a, b, c, d) {
  c + (1 - c) / (1 + exp(-1 * (theta - b)))
}

# Define the information function for a single item
information_1pl <- function(theta, a, b, c, d) {
  p <- prob_1pl(theta, a, b, c, d)
  q <- 1-p
  return(q * ((p-0.5)/0.5)^2 / p)
  
}

# Generate a sequence of theta values
theta_values <- seq(-4, 4, length.out = 100)

# Calculate the Test Information Function
test_information <- theta_values %>%
  map_dbl(function(theta) {
    items %>%
      mutate(info = information_1pl(theta, a, b, c, d)) %>%
      summarize(total_info = sum(info)) %>%
      pull(total_info)
  })

# Create a data frame for plotting
plot_data <- tibble(
  theta = theta_values,
  information = test_information
)

# Plot the Test Information Function
ggplot(plot_data, aes(x = theta, y = information)) +
  geom_line(color = "black", size = 1) +
  ylim(0, 20) + 
  labs(
    title = "Test information based on 246 items",
    x = "Theta ability",
    y = "Test information"
  )
}
```

```{r}
item.bank.real <- data.frame(df.word_params_new %>% 
  dplyr :: select(-c(word, ...1, corpusId)))

plot.test.information(df.word_params_new)
```

```{r}
ggplot(df.word_params_new %>% 
         dplyr :: rename(`Item type` = realpseudo), aes(x=b,  fill = `Item type`, color = `Item type`)) + geom_histogram(position = "identity", alpha = 0.7, bins = 20) + xlim(-4, 4) + 
  labs(x = "Item difficulty parameter",
       y = "Count") + 
  theme(legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        title = element_text(size = 15),
        axis.text=element_text(size= 15),
        axis.title=element_text(size=15))
  

ggsave("../plots/roar_cat_study1_figure5.png", width = 6, height = 5)
ggsave("../plots/roar_cat_study1_figure5.pdf", width = 6, height = 5)
```

# Get true mirt theta 
```{r}
colnames.order <- c(df.word_params_new$word)
```

```{r}
df.resp.identifier <- df.student.final %>% 
  dplyr :: select(pid, word, correct) %>% 
  pivot_wider(names_from = word, values_from = correct) %>% 
  dplyr :: select(pid)

df.resp <- df.student.final %>% 
  dplyr :: select(pid, word, correct) %>% 
  pivot_wider(names_from = word, values_from = correct) %>% 
  dplyr :: select(-pid) %>% 
  dplyr :: select(colnames(get(mirt0.2.order)))
```

```{r}
scores <- fscores(get(mirt0.2),  
                    method = "ML", 
                    full.scores.SE = T,
                    theta_lim = c(-4, 4),
                    min_theta= -4, 
                    max_theta = 4,
                    response.pattern = df.resp)
df.matrix <- as_tibble(scores)

df.estimate <- df.matrix %>%
    dplyr :: rename(trueEstimate = F1, trueSE = SE_F1) %>% 
  mutate(pid = df.resp.identifier$pid) %>% 
  mutate(trueEstimate = round(trueEstimate, digits = 6))
```
```{r}
scores.theta.6 <- fscores(get(mirt0.3),  
                    method = "ML", 
                    full.scores.SE = T,
                    theta_lim = c(-6, 6),
                    min_theta= -6, 
                    max_theta = 6,
                    response.pattern = df.resp)
df.matrix.theta.6 <- as_tibble(scores.theta.6)

df.estimate.new <- df.estimate %>% 
  mutate(trueEstimate.6 = df.matrix.theta.6$F1, trueSE.6 = df.matrix.theta.6$SE_F1) 
```


```{r}
ggplot(df.estimate.new, aes(x = trueEstimate)) +
  geom_histogram(binwidth = 0.5, fill = "grey", color = "black") +
  labs(title = "Distribution of theta estimate with limit (-4, 4)",
       x = "Theta estimate",
       y = "Count") + 
  theme(legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15),
        title = element_text(size = 15),
        axis.text=element_text(size= 15),
        axis.title=element_text(size=15))

```

Sanity Check: difference between using theta range (-4,4) vs (-6, 6)
```{r fig.width=8,fig.height=6}
g.theta.justification.1 <- ggplot(df.estimate.new , mapping = aes(x = trueEstimate,
                     y = trueEstimate.6)) +  
  geom_abline(color = 'gray', linetype = "dashed") +
  geom_point(size = 1) + 
  labs(x = "Theta estimate with limit (-4, 4)",
       y = "Theta estimate with limit (-6, 6)") + 
  xlim(-6, 6) + 
  ylim(-6, 6) + 
  coord_equal() + 
  theme(legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15),
        title = element_text(size = 15),
        axis.text=element_text(size= 15),
        axis.title=element_text(size=15))

g.theta.justification.2 <- ggplot(df.estimate.new, mapping = aes(x = trueSE,y = trueSE.6, color = trueEstimate.6)) +  
  geom_abline(color = 'gray', linetype = "dashed") + 
  geom_point(size = 1) +
  labs(x = "SEM with theta limit (-4, 4)",
       y = "SEM with theta limit (-6, 6)")  + scale_color_viridis(option = 'plasma') + 
  labs(color = "Theta estimate with limit (-6, 6)") + theme(legend.position = "bottom") + xlim(0, 1) +
  theme(legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15),
        title = element_text(size = 15),
        axis.text=element_text(size= 15),
        axis.title=element_text(size=15))

g.theta.justification <- g.theta.justification.1 + g.theta.justification.2 + plot_layout(ncol = 2)

ggsave("../plots/roar_cat_study2_SI_3.pdf", width = 10, height = 5)
ggsave("../plots/roar_cat_study2_SI_3.png", width = 10, height = 5)
  
```

# Obtain empirical response patterns with true theta esimate 
```{r}
colnames.order <- c("pid", df.word_params_new$word)

df.student.with.trueEstimate <- df.student.final %>% 
  left_join(df.estimate, by = "pid") 

df.validation.resp.adaptive <- df.student.with.trueEstimate %>% 
  filter(variant == "adaptive") %>% 
  dplyr :: select(pid, word, correct) %>% 
  pivot_wider(names_from = word, values_from = correct) %>% 
  dplyr ::select(colnames.order)

df.validation.resp.random <- df.student.with.trueEstimate %>% 
  filter(variant == "random") %>% 
  dplyr ::select(pid, word, correct) %>% 
  pivot_wider(names_from = word, values_from = correct) %>% 
  dplyr ::select(colnames.order)

df.validation.resp <- rbind(df.validation.resp.adaptive, df.validation.resp.random)
```

```{r}
#write.csv(df.validation.resp, "../data/roar_cat_validation_resp.csv")
```

```{r}
# df.validation.resp.renamed <- df.validation.resp %>%
#   arrange(pid) %>% 
#   mutate(pid_new = 1 : 478) %>%
#   select(-pid) %>%
#   relocate(pid_new)
# 
# write.csv(df.validation.resp.renamed, "../data/roar_cat_validation_renamed.csv")
```

# Theoretical Approach
## Prepare response patterns
```{r}
##we'll start small just so that you can see everything, but you'll want to make this bigger downstream.
ni<-246
np<-472
calibration.n <- 1500

df.theta.sample <- df.student.final %>% 
  filter(trialNumTotal == ni) %>% 
  dplyr :: select(pid, thetaEstimate)
```

```{r}
##now we're going to simulate data according to this model and examine some key properties
set.seed(1)
##first let's describe the individual level part of the model
th<-rnorm(calibration.n, mean = 0, sd = 1)
```

```{r}
################################################################
##now we have to put this stuff together. what we want is a probability of a correct response for a person to an item
##we're going to use what you may know from logistic regression

inv_logit<-function(x) {
  return (0.5 + 0.5 * (exp(x)/(1+exp(x))))
}
```

```{r}
func.create.response <- function(b, th, np, ni) {
  th.mat<-matrix(th,np,ni,byrow=FALSE) #these are the true abilities. we don't observe them,    which will be a real problem for us downstream. but we'll not worry about that today.
#th.mat #abilities, on per row
##now the item level part.
  b.mat <- matrix(rep(b, np), nrow = np, byrow = TRUE)

  pr<-inv_logit(th.mat-b.mat)

  resp <- pr

  for (i in 1:ncol(resp)) {
    resp[,i]<-rbinom(nrow(resp),1,resp[,i])
  }

  return (data.frame(resp))
}
```

```{r}
#th.sample <- th<-rnorm(np, mean = -0.8, sd = 1.5)
th.sample <- df.theta.sample$thetaEstimate
resp.sample <- func.create.response(item.bank.real$b, th.sample, np, ni)

monte.carlo.resp <- resp.sample %>% 
  mutate(pid = df.theta.sample$pid) %>% 
  relocate(pid)
```

```{r}
monte.carlo.resp.ordered <- setNames(monte.carlo.resp %>% dplyr :: select(-pid), df.word_params_new$word) %>% 
  dplyr :: select(colnames(get(mirt0.2.order)))
  
```

```{r}
th.sample.computed <- fscores(get(mirt0.2),  
                    method = "ML", 
                    full.scores.SE = T,
                    theta_lim = c(-4, 4),
                    min_theta= -4, 
                    max_theta = 4,
                    response.pattern = monte.carlo.resp.ordered)

monte.carlo.trueEstimate <- as_tibble(th.sample.computed) %>%
    dplyr :: rename(trueEstimate = F1, trueSE = SE_F1) %>% 
  mutate(pid = monte.carlo.resp$pid) %>% 
  mutate(trueEstimate = round(trueEstimate, digits = 6))

```

# CAT Simulation Functions
simulate participants
```{r}
set.seed(7)
func.catSim <- function(resp, item.bank, method){
  
  ni = length(resp)-1
  np = length(resp[[1]])
  list.thetas <- NULL
  list.se <- NULL
  list.pid <- NULL
  list.item <- NULL
  
  # define cat
  pids <- resp$pid
  resp <- resp %>% select(-pid)
  
  test <- list(method = 'ML', itemSelect = method, infoType = "Fisher")
  stop <- list(rule = 'length',thr = ni)
  final <- list(method = 'ML')
  cbList <- list(names = c("real", "pseudo"), props = c(0.5, 0.5))
  for (i in 1:np){
    pid <- pids[i]
    random_number <- sample(c(61, 177), size = 1)
    start <- list(fixItems = random_number, nrItems = 1, theta = 0)
    res <- randomCAT(itemBank = item.bank, 
                     responses = as.numeric(resp[i,]), 
                     start = start, 
                     test = test, 
                     final = final, 
                     stop = stop, 
                     cbControl = cbList)
    list.thetas <- c(list.thetas, res$thetaProv)
    list.pid <- c(list.pid, rep(pid, times = 246))
    list.se <- c(list.se, res$seProv)
    list.item <- c(list.item, res$testItems)
  }
  list.trialNumBlock <- rep(1:ni, np)
 
  return(data.frame(pid = list.pid, 
                    trialNumTotal = list.trialNumBlock, 
                    item = list.item,
                    thetaEstimate = list.thetas, 
                    thetaSE = list.se))
}
```

# Post-hoc Simulation in catR
```{r}
set.seed(1)
monte.carlo.cat.simulation <- function(df.theta.sample, item.bank, iteration){
  ni<-246
  np<-472
  th.sample <- df.theta.sample$thetaEstimate
  resp.sample <- func.create.response(item.bank$b, th.sample, np, ni)
  
  
  df <- resp.sample %>% 
    mutate(pid = df.theta.sample$pid) %>% 
    relocate(pid)
  
  df.results <- NULL
  for (i in 1:iteration) {
    print(i)
    df.shuffle <- df %>% 
      sample_n(size = n(), replace = FALSE)
    
    # Calculate the midpoint
    n_rows <- nrow(df.shuffle)
    midpoint <- ceiling(n_rows / 2)

    # Split the data frame into two halves
    half1 <- df.shuffle[1:midpoint, ]
    half2 <- df.shuffle[(midpoint + 1):n_rows, ]
    
    df.mfi.real <- func.catSim(half1, item.bank, "MFI")
    df.random.real <- func.catSim(half2, item.bank, "random")
    
    df.results <- df.results %>% 
      rbind(rbind(df.mfi.real %>% add_column(variant = "adaptive"), 
          df.random.real %>% add_column(variant = "random")) %>% 
      add_column(iteration = i)) 
  }
  return (df.results)
}
```

```{r}
df.monte.carlo.results.v2 <- monte.carlo.cat.simulation(df.theta.sample, item.bank.real, 5)
```

```{r}
#write.csv(df.monte.carlo.results.v2, "../data/catR_monte_carlo_simulation_v2.csv")
```
```{r}
df.monte.carlo.results.v2 <- read.csv("../data/catR_monte_carlo_simulation_v2.csv")
```

## simulation data 
```{r}
df.monte.carlo.simulation.compare <- df.monte.carlo.results.v2  %>%
   mutate(thetaEstimate = round(thetaEstimate, digits = 4)) %>%
  filter(trialNumTotal == 246) %>%
  dplyr :: select(pid, thetaEstimate) %>%
  dplyr :: rename(trueEstimate = thetaEstimate) %>%
  unique() %>% 
  left_join(df.monte.carlo.results.v2 %>%
  mutate(thetaEstimate = round(thetaEstimate, digits = 4)) %>% 
    unique())
```

```{r}
df.trueEstimate <- df.student.final %>%
   mutate(thetaEstimate = round(thetaEstimate, digits = 4)) %>% 
  filter(trialNumTotal == 246) %>% 
  dplyr :: select(pid, thetaEstimate) %>% 
  dplyr :: rename(trueEstimate = thetaEstimate)

df.compare.school <- df.student.final %>%
  mutate(thetaEstimate = round(thetaEstimate, digits = 4)) %>% 
  left_join(df.trueEstimate, by = "pid")

df.compare.all <- df.compare.school %>% add_column(type = "empirical", iteration = 1) %>% 
  dplyr ::select(pid, variant, trialNumTotal, type, thetaEstimate, iteration, thetaSE, trueEstimate) %>% 
  rbind(df.monte.carlo.simulation.compare %>% add_column(type = "simulation") %>% 
  dplyr ::select(pid, variant, trialNumTotal, type, thetaEstimate, iteration, thetaSE, trueEstimate)) %>% unique() %>% 
  mutate(variant = ifelse(variant == "adaptive", "ROAR-CAT", "ROAR-Random"))
```

```{r}
quintiles <- quantile(df.compare.school$trueEstimate, probs = c(0, 0.20, 0.40, 0.60, 0.80, 1))

quintiles
```

```{r}
func.visualize.differences.validate.bin <- function(df.compare, quintiles){
 

  df.simulation.true.data.2 <- df.compare %>%
    mutate(theta.bin = cut(trueEstimate, breaks = quintiles, include.lowest = TRUE, labels = c("Q1", "Q2", "Q3", "Q4", "Q5"))) %>% 
    filter(!is.na(theta.bin))
  
  df.plot_curve <- df.simulation.true.data.2 %>%
    group_by(variant, type, trialNumTotal, theta.bin) %>%
    dplyr::summarise(sem = mean(thetaSE), 
                     reliability = empirical_rxx(as.matrix(tibble(F1 = thetaEstimate, SE_F1 = thetaSE))),
                     mse = Metrics :: mse(trueEstimate, thetaEstimate), 
                     bias = Metrics :: bias(trueEstimate, thetaEstimate)) 
   
  return (df.plot_curve %>% ungroup())
}

func.visualize.differences.validate.all <- function(df.compare, list.trueEstimate){
  
  df.plot_curve <- df.compare %>%
    group_by(variant, type, trialNumTotal) %>%
    dplyr::summarise(sem = mean(thetaSE), 
                     reliability = empirical_rxx(as.matrix(tibble(F1 = thetaEstimate, SE_F1 = thetaSE))),
                     mse = Metrics :: rmse(trueEstimate, thetaEstimate), 
                     cor = cor(trueEstimate, thetaEstimate), 
                     bias = Metrics :: bias(trueEstimate, thetaEstimate)) #%>% 
   
  return (df.plot_curve %>% ungroup())
}
```


```{r}
quintiles <- quantile(df.compare.school$trueEstimate, probs = c(0, 0.20, 0.40, 0.60, 0.80, 1))
df.aggregrate.learning.curve <- func.visualize.differences.validate.bin(df.compare.all, quintiles) 
df.aggregrate.learning.curve.all <- func.visualize.differences.validate.all(df.compare.all, df.estimate$trueEstimate)
```

## sanity check of SEM
```{r}
df.check.first.10.trials <- df.compare.all %>% 
  filter(trialNumTotal <= 10, type == "empirical")

summary_df <- df.check.first.10.trials %>%
  group_by(trialNumTotal, variant) %>%
  dplyr :: summarise(
    mean_thetaSE = mean(thetaSE),
    sd_thetaSE = sd(thetaSE) 
  )

ggplot(summary_df, aes(x = trialNumTotal, y = mean_thetaSE, color = variant)) +
  geom_point(position = position_dodge(width = 0.2), size = 2) +
  geom_errorbar(aes(ymin = mean_thetaSE - sd_thetaSE, ymax = mean_thetaSE + sd_thetaSE),
                width = 0.2, position = position_dodge(width = 0.2)) +
   scale_x_continuous(breaks = seq(1, 10, by = 1), labels = seq(1, 10, by = 1)) +
  labs(title = "Standard error of measurement of theta estimate (mean and standard deviation)",
       x = "Number of test items",
       y = "Standard error of measurement of theta estimate",
       color = "Variant") 
```


# Results
## reliability

```{r fig.width=6,fig.height=6}
df.aggregrate.learning.curve.all$type <- factor(df.aggregrate.learning.curve.all$type, levels = c("simulation", "empirical"))
g.reliability.all <- ggplot(df.aggregrate.learning.curve.all %>% filter(type == "empirical"), mapping = aes(x = trialNumTotal, y = reliability)) +
  geom_smooth(aes(linetype = variant), color = "black", size = 2, se = FALSE) +
  labs(x = "Number of test items", 
       y = "Reliability",
       title = "Empirical Test Reliability") +
  ylim(0,1) +
  xlim(1, 246) + 
  scale_y_continuous(breaks = round(seq(0, 1, by = 0.1),1)) +
  scale_color_manual(values=c("#8F993E", "#E05A1D")) + 
  theme(title = element_text(
        size = 20, color = "black"), 
        legend.text = element_text(size = 18), 
        legend.title = element_text(size = 18, face = "bold"),
        axis.text=element_text(size=18),
        plot.margin = margin(1,1,1,1, "cm"),
        #panel.spacing = unit(1, "lines"), 
       # panel.grid = element_line(size = 2), 
        legend.key.size = unit(2, "lines"),
        axis.title=element_text(size=20), legend.position = "none")

```

## MSE
```{r fig.width=6,fig.height=6}

g.mse.all <- ggplot(df.aggregrate.learning.curve.all %>% filter(type == "empirical"), mapping = aes(x = trialNumTotal,
                     y = mse)) +
  geom_smooth(aes(linetype = variant), color = "black", size = 2, se = FALSE) +
  labs(x = "Number of test items",
       y = "Mean squared error",
       title = "Mean Squared Error") + 
  ylim(0, 1) +
  xlim(1, 246) + 
  scale_color_manual(values=c("#8F993E", "#E05A1D")) + 
  theme(title = element_text(
        size = 20, color = "black"), 
        legend.text = element_text(size = 18), 
        legend.title = element_text(size = 18, face = "bold"),
        axis.text=element_text(size=18),
        plot.margin = margin(1,1,1,1, "cm"),
        #panel.spacing = unit(1, "lines"), 
       # panel.grid = element_line(size = 2), 
        legend.key.size = unit(2, "lines"),
        axis.title=element_text(size=20), legend.position = "none")
``` 

## bias
```{r fig.width=6,fig.height=6}

g.bias.all <- ggplot(df.aggregrate.learning.curve.all %>% filter(type == "empirical"), mapping = aes(x = trialNumTotal,
                     y = bias)) +
  geom_smooth(aes(linetype = variant), color = "black", size = 2, se = FALSE) +
  labs(x = "Number of test items",
       y = "Bias",
       title = "Bias") +
  xlim(1, 246) + 
  scale_color_manual(values=c("#8F993E", "#E05A1D")) + 
  theme(title = element_text(
        size = 20, color = "black"), 
        legend.text = element_text(size = 18), 
        legend.title = element_blank(),
        axis.text=element_text(size=18),
        plot.margin = margin(1,1,1,1, "cm"),
        #panel.spacing = unit(1, "lines"), 
       # panel.grid = element_line(size = 2), 
        legend.key.size = unit(2, "lines"),
        axis.title=element_text(size=20), legend.position = "bottom")
```

```{r }
g.reliability.all + g.bias.all + g.mse.all

ggsave("../plots/roar_cat_study2_figure2.png", width=15,height=6)
ggsave("../plots/roar_cat_study2_figure2.pdf", width=15,height=6)
```


## analysis based on 5 bins

```{r}
# df.aggregrate.learning.curve$theta.bin <- factor(df.aggregrate.learning.curve$theta.bin, levels = c("low theta", "medium theta", "high theta"))
df.aggregrate.learning.curve$type <- factor(df.aggregrate.learning.curve$type, levels = c("simulation", "empirical"))
g.sem <- ggplot(df.aggregrate.learning.curve , mapping = aes(x = trialNumTotal,
                     y = sem,  
                     color = type, 
                     linetype = variant)) +
  geom_smooth(size = 2, se = FALSE) +
  labs(x = "Number of test items",
       y = "Standard error of measurement",
       title = "Standard Error of Measurement") +
  ylim(0.25, 1.5) +
  xlim(1, 150) +
  facet_grid(cols = vars(theta.bin)) + 
  scale_color_manual(values=c("#8F993E", "#E05A1D")) + 
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))

g.mse <- ggplot(df.aggregrate.learning.curve , mapping = aes(x = trialNumTotal,
                     y = mse,  
                     color = type, 
                     linetype = variant)) +
  geom_smooth(size = 2, se = FALSE) +
  labs(x = "Number of test items",
       y = "Mean squared error",
       title = "Mean Squared Error") +
  ylim(0, 1) +
  xlim(1, 150) +
  facet_grid(cols = vars(theta.bin)) + 
  scale_color_manual(values=c( "#8F993E", "#E05A1D")) +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))

g.bias <- ggplot(df.aggregrate.learning.curve , mapping = aes(x = trialNumTotal,
                     y = bias,
                     color = type, 
                     linetype = variant)) +
  geom_smooth(size = 2, se = FALSE) +
  labs(x = "Number of test items",
       y = "Bias",
       title = "Bias") +
   xlim(1, 150) +
  ylim(-0.75, 0.75) +
  facet_grid(cols = vars(theta.bin)) +
  scale_color_manual(values=c("#8F993E", "#E05A1D")) +
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))
```

### empirical vs. catR simulation 
```{r}
(g.sem + theme(strip.text =element_text(
        size = 20, color = "black"),
        title = element_text(
        size = 20, color = "black"), 
        legend.text = element_text(size = 18), 
        legend.title = element_text(size = 18, face = "bold"),
        axis.text=element_text(size=20),
        plot.margin = margin(1,1,1,1, "cm"),
        panel.spacing = unit(1, "lines"), 
        #panel.grid = element_line(size = 2), 
        axis.title=element_text(size=20), legend.position = "none")) /
  (g.bias + theme(title = element_text(
        size = 20, color = "black"), 
        strip.text = element_text(
        size = 20, color = "black"),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 18, face = "bold"),
        axis.text=element_text(size=20),
        plot.margin = margin(1,1,1,1, "cm"),
        panel.spacing = unit(1, "lines"), 
        #panel.grid = element_line(size = 2), 
        axis.title=element_text(size=20), legend.position = "none")) /
( g.mse +
  theme(strip.text = element_text(
        size = 20, color = "black"),
        title = element_text(
        size = 20, color = "black"), 
        legend.text = element_text(size = 18), 
        #legend.title = element_text(size = 18, face = "bold"),
        axis.text=element_text(size=20),
        plot.margin = margin(1,1,1,1, "cm"),
        panel.spacing = unit(1, "lines"), 
        legend.key.size = unit(4, "lines"),
        #panel.grid = element_line(size = 2),
        legend.title = element_text(size = 18, face = "bold"),
        axis.title=element_text(size=20), legend.position = "bottom")) 


ggsave("../plots/roar_cat_study2_SI_3.png", width=15, height=15)
ggsave("../plots/roar_cat_study2_SI_3.pdf", width=15, height=15)
```

### empirical only

```{r}
df.aggregrate.learning.curve.empirical <- df.aggregrate.learning.curve %>% 
  filter(type == "empirical")

g.sem <- ggplot(df.aggregrate.learning.curve.empirical , mapping = aes(x = trialNumTotal,
                     y = sem,  
                     linetype = variant)) +
  geom_smooth(size = 2, se = FALSE, color = "#E05A1D") +
  labs(x = "Number of test items",
       y = "Standard error of measurement",
       title = "Standard Error of Measurement") +
  ylim(0.25, 1.5) +
  xlim(1, 150) +
  facet_grid(cols = vars(theta.bin)) + 
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))

g.mse <- ggplot(df.aggregrate.learning.curve.empirical , mapping = aes(x = trialNumTotal,
                     y = mse,  
                     linetype = variant)) +
  geom_smooth(size = 2, se = FALSE, color = "#E05A1D") +
  labs(x = "Number of test items",
       y = "Mean squared error",
       title = "Mean Squared Error") +
  ylim(0, 1) +
  xlim(1, 150) +
  facet_grid(cols = vars(theta.bin)) +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))

g.bias <- ggplot(df.aggregrate.learning.curve.empirical , mapping = aes(x = trialNumTotal,
                     y = bias,
                     linetype = variant)) +
  geom_smooth(size = 2, se = FALSE, color = "#E05A1D") +
  labs(x = "Number of test items",
       y = "Bias",
       title = "Bias") +
   xlim(1, 150) +
  ylim(-0.75, 0.75) +
  facet_grid(cols = vars(theta.bin)) +
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))

(g.sem + theme(strip.text =element_text(
        size = 20, color = "black"),
        title = element_text(
        size = 20, color = "black"), 
        legend.text = element_text(size = 18), 
        legend.title = element_text(size = 18, face = "bold"),
        axis.text=element_text(size=20),
        plot.margin = margin(1,1,1,1, "cm"),
        panel.spacing = unit(1, "lines"), 
        #panel.grid = element_line(size = 2), 
        axis.title=element_text(size=20), legend.position = "none")) /
(g.bias + 
  theme(strip.text = element_text(
        size = 20, color = "black"),
        title = element_text(
        size = 20, color = "black"), 
        legend.text = element_text(size = 18), 
        legend.title = element_text(size = 18, face = "bold"),
        axis.text=element_text(size=20),
        plot.margin = margin(1,1,1,1, "cm"),
        panel.spacing = unit(1, "lines"), 
        #panel.grid = element_line(size = 2), 
        axis.title=element_text(size=20), legend.position = "none")) / (g.mse + theme(title = element_text(
        size = 20, color = "black"), 
        strip.text = element_text(
        size = 20, color = "black"),
        legend.text = element_text(size = 18),
        legend.key.size = unit(4, "lines"),
        axis.text=element_text(size=20),
        plot.margin = margin(1,1,1,1, "cm"),
        panel.spacing = unit(1, "lines"), 
        #panel.grid = element_line(size = 2), 
        legend.title = element_text(size = 18, face = "bold"),
        axis.title=element_text(size=20), legend.position = "bottom"))

ggsave("../plots/roar_cat_study2_figure3.png", width=15, height=15)
ggsave("../plots/roar_cat_study2_figure3.pdf", width=15, height=15)
```


# Exploratory Analysis

```{r}
quartiles <- quantile(df.compare.all$trueEstimate, probs = c(0, 0.20, 0.40, 0.60, 0.80, 1))

df.wrong.estimate <- df.compare.all %>% 
    mutate(theta.bin = cut(trueEstimate, breaks = quartiles, include.lowest = TRUE, labels = c("Q1", "Q2", "Q3", "Q4", "Q5"))) %>% 
  filter(trialNumTotal %in% c(80)) %>% 
  group_by(pid, type, trialNumTotal, theta.bin) %>% 
  dplyr ::summarise(thetaSE = mean(thetaSE),thetaEstimate = mean(thetaEstimate), trueEstimate = mean(trueEstimate)) %>% 
  mutate(diff = abs(trueEstimate - thetaEstimate)) %>% 
  dplyr :: select(-c(trueEstimate, thetaEstimate, thetaSE)) %>% 
  pivot_wider(names_from = type, values_from = diff) %>% 
  filter(abs(simulation-empirical) > 1)
```

```{r}
df.compare.school %>% 
  filter(trueEstimate < -1.02, trueEstimate > -2.3) %>% 
  filter(variant == "random") %>% 
  group_by(block) %>% 
  dplyr :: summarise(mean(correct), sd(correct))

df.compare.school %>% 
  filter(trueEstimate < -0.26, trueEstimate > -1.02) %>% 
  filter(variant == "random") %>% 
  group_by(block) %>% 
  dplyr :: summarise(mean(correct), sd(correct))
```

```{r}
quartiles <- quantile(df.compare.school$trueEstimate, probs = c(0, 0.20, 0.40, 0.60, 0.80, 1))

df.wrong.estimate <-df.student.final %>% 
  mutate(thetaEstimate = round(thetaEstimate, digits = 4)) %>% 
  left_join(df.trueEstimate, by = "pid") %>% 
  mutate(theta.bin = cut(trueEstimate, breaks = quartiles, include.lowest = TRUE, labels = c("Q1", "Q2", "Q3", "Q4", "Q5"))) %>% 
  #filter(theta.bin %in% c("Q2", "Q3")) %>% 
  dplyr ::select(pid, variant, rt, word, realpseudo, difficulty, theta.bin, correct, block, trialNumTotal, thetaEstimate, thetaSE, trueEstimate) %>% 
  mutate(response = ifelse(((realpseudo == "real") & (correct == 1)) | ((realpseudo == "pseudo") & (correct == 0)), "right", "left")) %>% 
  filter(theta.bin == "Q2") %>% 
  filter(trialNumTotal == 60) %>% 
  filter(abs(thetaEstimate - trueEstimate) > 1.5)
```

