---
title: "ROAR-CAT: Parameter Invariance Study"
author: "Wanjing Anya Ma"
date:  "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
---

# Load packages

```{r, message=FALSE, warning = FALSE, echo = FALSE}
library("knitr") # for rendering the RMarkdown file
library("tidyverse") # for data wrangling 
library(dplyr)
library(mirt)
library('ggpubr')
library(Metrics)
library(hash)
library(ggplot2)
library(GGally)
library(gridExtra)
library("catR")
library(cocor)
library(eRm)
library(difR)
library(extrafont)
library(here)
```

# Settings

```{r echo = FALSE}
# sets how code looks in knitted document
opts_chunk$set(comment = "")

# suppresses warning about grouping 
options(dplyr.summarise.inform = F)
```

# Data

## Data Loading
```{r message = FALSE, warning = FALSE, results='hide'}
df.data <- read_csv(here::here('data/school/roar_swr_rp_grouped_anonymized.csv')) %>% filter(groupId != "D", session == 1)

df.data.rt <-  read_csv(here::here('data/school/roar_swr_rp_grouped_anonymized_rt.csv')) %>% filter(groupId != "D", session == 1)

df.word_params <- read_csv(here::here('corpus/item_bank_v2.csv'))
```

## Data wrangling 
```{r}
df.word_params.dic <- df.word_params %>% 
  dplyr :: rename(word = words) %>% 
  select(word, realpseudo)
```

## Identify if rt-removal makes sense? (Decision: no big difference, so we keep all data)
```{r}
df.data.rt.long <- df.data.rt %>% 
  pivot_longer(
    cols = starts_with("rt."),  # Specify columns to pivot
    names_to = "word",      # New column for names
    names_prefix = "rt.",  
    values_to = "rt"     # New column for values
  ) %>% 
  mutate(log_rt = log(rt))

ggplot(df.data.rt.long, aes(x = log_rt)) +
  geom_density() +
  labs(title = "Density Plot", x = "Value", y = "Density") +
  theme_minimal()

df.data.rt.summary.person <- df.data.rt %>% 
  pivot_longer(
    cols = starts_with("rt."),  # Specify columns to pivot
    names_to = "word",      # New column for names
    names_prefix = "rt.",  
    values_to = "rt"     # New column for values
  ) %>% 
  group_by(pid, groupId) %>% 
  dplyr::summarise(median_log_rt = median(log(rt)))

df.group.specific.threshold <- df.data.rt.summary.person %>% 
  group_by(groupId) %>% 
  dplyr::summarise(mean_value = mean(median_log_rt), sd_value = sd(median_log_rt)) %>% 
  mutate(threshold_lower = mean_value - 3*sd_value, threshold_upper = mean_value + 3*sd_value)

df.data.rt.summary.person.exclude <- df.data.rt.summary.person %>% 
  left_join(df.group.specific.threshold) %>% 
  filter(median_log_rt < threshold_lower | median_log_rt > threshold_upper) %>% 
  filter(!groupId %in% c("Calibration"))

df.data.with.valid.resp <- df.data.rt %>% 
  pivot_longer(
    cols = starts_with("rt."),  # Specify columns to pivot
    names_to = "word",      # New column for names
    names_prefix = "rt.",  
    values_to = "rt"     # New column for values
  ) %>% 
  left_join(
  df.data %>% 
  pivot_longer(
    cols = starts_with("correct."),  # Specify columns to pivot
    names_to = "word",      # New column for names
    names_prefix = "correct.",  
    values_to = "correct"     # New column for values
  )) %>% 
  filter(rt >= 200, rt <= 5000) %>% 
  select(-rt) %>% 
  arrange(word) %>% 
  pivot_wider(names_from = word, values_from = correct, names_prefix = "correct.") 

```

# Rasch Model 
```{r message = FALSE, warning = FALSE, results='hide'}
df.response.calibration <- df.data %>% 
    filter(groupId == 'Calibration') %>% 
    select(-c(pid, ageMonths, groupId, subGroup, grade, session))

r.m.g.calibration <- mirt(df.response.calibration, 1, itemtype = "Rasch", guess = 0.5, SE = TRUE, 
              technical = list(NCYCLES = 5000))
```

# Prepare Item Parameters
```{r message = FALSE, warning = FALSE, results='hide'}
func.estimate <- function(df, id){
  df.response <- df %>% 
    filter(groupId == id) %>% 
    select(-c(ageMonths, groupId, subGroup, grade, session))
  scores <- fscores(r.m.g.calibration, response.pattern = df.response %>% select(-pid), theta_lim = c(-4, 4))
  df.matrix <- as_tibble(scores)
  df.estimate <- df.matrix %>% 
    dplyr :: rename(thetaEstimate = F1, thetaSE = SE_F1) %>% 
    add_column(pid = df.response$pid, groupId = id) %>% 
    select(pid, everything())
  
  return (df.estimate)
}
```

```{r message = FALSE, warning = FALSE, results='hide'}
func.estimate.thetas.groups <- function(df){
  df.thetas.calibration <- func.estimate(df, 'Calibration')
  df.thetas.A <- func.estimate(df, 'A')
  df.thetas.B <- func.estimate(df, 'B')
  df.thetas.C <- func.estimate(df, 'C')
  df.thetas <- do.call("rbind", list(df.thetas.calibration , df.thetas.A, df.thetas.B, df.thetas.C))
  return (df.thetas)
}

df.thetas <- func.estimate.thetas.groups(df.data)
```


```{r message = FALSE, warning = FALSE, results='hide'}
rasch.model.params <- function (df, id) {
  df.response <- df %>% 
    filter(groupId == id) %>% 
    select(-c(pid, ageMonths, groupId, subGroup, grade, session))
  
  r.m.g <- mirt(df.response, 1, itemtype = "Rasch", guess = 0.5, SE = TRUE, 
              technical = list(NCYCLES = 200))
  
  params <- data.frame(coef(r.m.g, IRTpars = TRUE, simplify = TRUE))$items.b
  
  return (params)
}
```

```{r message = FALSE, warning = FALSE, results='hide'}
create.params.table <- function(df) {
  df.result <- df %>% 
    filter(pid == df$pid[1]) %>% 
    select(-c(pid, ageMonths, groupId, subGroup, grade, session)) %>% 
    pivot_longer(cols= everything(), 
                 names_prefix = "correct.", 
                 names_to = "word") %>% 
    select(word)
  
  list.names <- c("Calibration", "A", "B", "C")
  for (i in (1: 4)) {
    print(i)
    df.result <- df.result %>% 
      add_column("{list.names[i]}":=rasch.model.params(df, list.names[i]))
  }
  return (df.result)
}
```

```{r message = FALSE, warning = FALSE, results='hide'}
df.params <- create.params.table(df.data)
```

```{r}
df.params.ready <- df.word_params %>% 
  dplyr :: rename(word = words) %>% 
  right_join(df.params, by = "word") %>% 
  arrange(word) %>% 
  relocate(word, Calibration, A, B, C)
```

```{r}
df.calibration.thetas <- df.thetas %>% filter(groupId == "Calibration")
hist(df.params$Calibration)
hist(df.calibration.thetas$thetaEstimate)
```


```{r}
df.params.ready.longer <- df.params.ready %>% 
  pivot_longer(c('A','B','C'), names_to = "groupId", values_to = "b.param")
```

# Item Parameter Distribution
```{r}
ggplot(df.params.ready) + 
  geom_histogram(aes(x = Calibration), color="black", fill="grey", bins = 20) + 
  facet_grid(rows = vars(realpseudo), switch = "both") + 
  labs(x = "item difficulty",
       y = "count") + 
  theme(strip.text.y = element_text(
        size = 12, color = "black"), 
        axis.text=element_text(size=12), 
        axis.title=element_text(size=12))
```

# Visualizations
## Discriptive Stats 
```{r}
group.names <- c("Calibration" = "Calibration", 
                 "A" = "Marigold", 
                 "B" = "Orchid", 
                 "C" = "Snowdrops")

group.names.sample.size <- c("Calibration" = "Calibration n = 306", 
                 "A" = "Marigold n = 1248", 
                 "B" = "Orchid n = 476", 
                 "C" = "Snowdrops n = 109")

df.data.renamed <- df.data %>% 
  filter(session == 1) %>% 
  mutate(groupId = group.names[groupId]) %>% 
  mutate(age = round(ageMonths/12, digits = 0))
```


```{r}
df.data.rt.summary <- df.data.rt %>% 
  filter(session == 1) %>% 
  pivot_longer(cols = contains("rt."), names_to = "word", values_to = "rt") %>%
  mutate(word = substring(word, 4,)) %>% 
  filter(rt >= 200, rt <= 5000, groupId != "D") %>% 
  group_by(pid) %>% 
  dplyr :: summarise(mean_rt = mean(rt))

df.descriptive.stats <- df.data.renamed %>% 
  select(pid, ageMonths) %>% 
  inner_join(df.thetas, by = c("pid")) %>% 
  inner_join(df.data.rt.summary, by = c("pid")) %>% 
  relocate(pid, groupId, ageMonths, thetaEstimate, thetaSE, mean_rt) %>% 
  mutate(groupId = group.names[groupId], mean_rt_log = log(mean_rt), age = ageMonths/12) 

df.descriptive.stats.longer.table <- df.descriptive.stats %>% 
  pivot_longer(cols = c("thetaEstimate", "thetaSE", "mean_rt_log", "age"), 
               names_to = "metric", 
               values_to = "value")

df.descriptive.stats.longer.plot <- df.descriptive.stats %>% 
  pivot_longer(cols = c("ageMonths", "thetaEstimate", "thetaSE", "mean_rt_log"), 
               names_to = "metric", 
               values_to = "value")
```

```{r}
df.descriptive.stats.summary <- df.descriptive.stats.longer.table %>% 
  group_by(metric, groupId) %>% 
  summarise(n = n(), mean = median(value, na.rm = TRUE), sd = sd(value, na.rm = TRUE))

```


```{r}
custom_labeller <- labeller(metric = c(ageMonths = "age (months)", 
                       mean_rt_log = "mean response time (ms) in log scale", 
                       thetaEstimate = "theta estimate", 
                       thetaSE = "standard error of theta estimate"))
```

```{r}
g.figure.study1.2 <- ggplot(df.descriptive.stats.longer.plot %>% 
  filter((groupId != "Calibration") | (value < 240)),
       aes(x = groupId,
           y = value,
           color = groupId)) +
  labs(y = "Metric",
       x = "Groups", 
       color = "Groups") +
  geom_boxplot(width = 0.3, na.rm = TRUE) +
  
  # geom_jitter(position=position_jitter(w=0.2, h=0.1), size = 0.5) +
  # geom_errorbar(data = df.descriptive.stats.summary , mapping = aes(x = groupId, y = mean, ymin = mean - sd, ymax = mean + sd), size=0.4, color="black", width=.1, facet_wrap = ~metric) +
  # geom_point(data = df.descriptive.stats.summary, aes(x = groupId, y = mean), size=1.5, color="black", facet_wrap = ~metric) +
  facet_wrap(~metric, scales = "free", labeller = custom_labeller) +
  theme(legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15),
        strip.text = element_text(size = 15),
        title = element_text(size = 15),
        axis.text=element_text(size= 15),
        axis.title=element_text(size=15), 
        axis.text.x = element_text(angle = 30, hjust = 1),
        legend.position = "bottom")


ggsave("../plots/roar_cat_study1_figure2.png", width = 10, height = 8)
ggsave("../plots/roar_cat_study1_figure2.pdf", width = 10, height = 8)

```


# Parameter Invariance

## group Effect: item difficulty

```{r}
function.compare.params <- function(df, group1, group2, type){
  df.tmp <- df %>% 
    filter(realpseudo == type)
  
  x <- df.tmp[[group1]] 
  y <- df.tmp[[group2]]
  
  correlation <- round(cor(x, y), digit = 2)

# Perform linear regression
  lm_model <- lm(y ~ x)

# Extract the slope and intercept
  slope <- round(coef(lm_model)[[2]], digit = 2)
  intercept <- round(coef(lm_model)[[1]], digit = 2)
  
  return (c(group1, group2, type, correlation, slope, intercept))
  
}
```

```{r fig.width=26,fig.height=16}
# Add sample size 
g.item.difficulty <- ggplot(df.params.ready.longer %>% mutate(groupId = group.names[groupId]) %>% dplyr :: rename(`item type` = realpseudo), mapping = aes(x = Calibration,
                     y = b.param, color = `item type`, group = `item type`)) +
  labs(x = "Item difficulty parameter from calibration",
       y = "Item difficulty parameter from group") +
  facet_grid(cols = vars(groupId)) + 
  stat_cor(cor.coef.name = 'r', aes(label = ..r.label..), size = 15) +
  # stat_cor(aes(label = paste("spearman", ..r.label.., sep = ":")), method = "spearman", vjust = 1) + 
  #stat_cor(aes(label = ..r.label..), method = "pearson") +
  theme(legend.position="bottom") +
  geom_text(aes(label = as.character(word)), hjust=0.4, vjust=0, size = 8) + 
  geom_abline(slope=1, intercept = 0, color = "grey", linetype = "dotted", size = 5) + 
  #xlim(-4, 5) + ylim(-4, 8) +
  scale_y_continuous(breaks = round(seq(-4, 13, by = 2),1)) +
  scale_x_continuous(breaks = round(seq(-4, 5, by = 2),1)) +
  theme(legend.text = element_text(size = 36), 
        legend.title = element_text(size = 36),
        strip.text = element_text(
        size = 36, color = "black"),
        axis.text=element_text(size=36),
        strip.text.y = element_text(
        size = 36, color = "black"), 
        panel.spacing = unit(6, "lines"), 
        legend.spacing = unit(6.0,'cm'), 
        plot.margin = margin(1.5,1.5,1.5,1.5, "cm"),
        axis.title=element_text(size=36), legend.position = "bottom") 
  g.item.difficulty
  
ggsave("../plots/roar_cat_study1_figure3.png")
ggsave("../plots/roar_cat_study1_figure3.pdf")
  
```
```{r}
ggplot(df.params.ready.longer %>% mutate(groupId = group.names[groupId]) %>% dplyr :: rename(`item type` = realpseudo) %>% filter(`item type` == "pseudo"), mapping = aes(x = Calibration,
                     y = b.param, color = `item type`, group = `item type`)) +
  labs(x = "Item difficulty parameter from calibration",
       y = "Item difficulty parameter from group") +
  facet_grid(cols = vars(groupId)) + 
  stat_cor(cor.coef.name = 'r', aes(label = ..r.label..)) +
  # stat_cor(aes(label = paste("spearman", ..r.label.., sep = ":")), method = "spearman", vjust = 1) + 
  #stat_cor(aes(label = ..r.label..), method = "pearson") +
  theme(legend.position="bottom") +
  geom_text(aes(label = as.character(word)), hjust=0.4, vjust=0, size = 1.5) + 
  geom_abline(slope=1, intercept = 0, color = "grey", linetype = "dotted", size = 1) + 
  #xlim(-4, 5) + ylim(-4, 8) +
  scale_y_continuous(breaks = round(seq(-4, 13, by = 2),1)) +
  scale_x_continuous(breaks = round(seq(-4, 5, by = 2),1))
```

### demo: an example of parameter invariance
```{r}
df.params.ready %>% 
  filter(word %in% c("ggnoi", "hust")) %>% 
  pivot_longer(cols = c("Calibration", "A", "B", "C")) %>% 
  select(name, word, value) %>% 
  pivot_wider(names_from = c("word"), values_from = "value") %>% 
  mutate(diff = ggnoi - hust)
```

```{r}
df.params.ready.longer %>% 
  filter(word == "rackle")
```

### remove item outlier 
```{r}
df.data.without.bad.items <- df.data %>% 
  select(-c(correct.an, correct.rackle, correct.potent, correct.garment, correct.bads, correct.streat))
```

```{r}
df.params.without.bad.items <- create.params.table(df.data.without.bad.items %>% filter(session == 1))
```
```{r}
df.params.ready.with.exclusion <- df.word_params %>% 
  dplyr :: rename(word = words) %>% 
  right_join(df.params.without.bad.items, by = "word") %>% 
  arrange(word) %>% 
  relocate(word, Calibration, A, B, C)

df.params.ready.longer.with.exclusion <- df.params.ready.with.exclusion %>% 
  pivot_longer(c('A','B','C'), names_to = "groupId", values_to = "b.param")

```

```{r fig.width=25,fig.height=15}
# Add sample size 
g.item.difficulty <- ggplot(df.params.ready.longer.with.exclusion %>% mutate(groupId = group.names[groupId]) %>% dplyr :: rename(`item type` = realpseudo), mapping = aes(x = Calibration,
                     y = b.param, color = `item type`, group = `item type`)) +
  labs(x = "Item difficulty parameter from calibration",
       y = "Item difficulty parameter from group") +
  facet_grid(cols = vars(groupId)) + 
  stat_cor(cor.coef.name = 'r', aes(label = ..r.label..), size = 15) +
  theme(legend.position="bottom") +
  geom_text(aes(label = as.character(word)), hjust=0.4, vjust=0, size = 8) + 
  geom_abline(slope=1, intercept = 0, color = "grey", linetype = "dotted", size = 5) + 
  scale_y_continuous(breaks = round(seq(-4, 13, by = 2),1)) +
  scale_x_continuous(breaks = round(seq(-4, 5, by = 2),1)) +
  theme(legend.text = element_text(size = 36), 
        legend.title = element_text(size = 36),
        strip.text = element_text(
        size = 36, color = "black"),
        axis.text=element_text(size=36),
        strip.text.y = element_text(
        size = 36, color = "black"), 
        panel.spacing = unit(6, "lines"), 
        legend.spacing = unit(6.0,'cm'), 
        plot.margin = margin(1.5,1.5,1.5,1.5, "cm"),
        axis.title=element_text(size=36), legend.position = "bottom") 
  g.item.difficulty
  
```

## group effect: response time 
```{r}
df.rt.exclusion.summary <- df.data.rt %>% 
  filter(session == 1) %>% 
  pivot_longer(cols = contains("rt."), names_to = "word", values_to = "rt") %>%
  mutate(word = substring(word, 4,)) %>% 
  mutate(valid= ifelse((rt < 200 | rt > 5000), 0 , 1)) %>% 
  group_by(valid) %>% 
  tally() %>% 
  mutate(percent = (n / sum(n)) * 100)

df.rt.exclusion.summary
```

```{r }
df.data.rt.grouped <- df.data.rt %>% 
  filter(session == 1) %>% 
  pivot_longer(cols = contains("rt."), names_to = "word", values_to = "rt") %>%
  mutate(word = substring(word, 4,)) %>% 
  filter(rt >= 200, rt <= 5000, groupId != "D") %>% 
  group_by(groupId, word) %>% 
  dplyr :: summarise(mean_rt = mean(log(rt))) 

df.data.rt.ready <- df.data.rt.grouped %>% 
  filter(groupId != "Calibration") %>% 
  left_join(df.data.rt.grouped %>% 
  filter(groupId == "Calibration"), by = "word") %>% 
  dplyr :: rename(Calibration = mean_rt.y, rt = mean_rt.x, groupId = groupId.x) %>% 
  select(-groupId.y) %>% 
  left_join(df.word_params.dic, by = "word")
```

```{r}
df.params.rt <- df.data.rt.grouped %>% 
  pivot_wider(names_from = groupId, values_from = mean_rt) %>% 
  left_join(df.word_params.dic, by = "word")
```

```{r fig.width=25,fig.height=15}
g.response.time <- ggplot(df.data.rt.ready %>% mutate(groupId = group.names[groupId]), mapping = aes(x = Calibration,
                     y = rt, color = realpseudo, group = realpseudo)) +
  labs(x = "Mean log response time (ms) from calibration",
       y = "Mean log response time (ms) from group") +
  facet_grid(cols = vars(groupId)) + 
  stat_cor(cor.coef.name = 'r', aes(label = ..r.label..), size = 15) +
  theme(legend.position="bottom") +
  geom_text(aes(label = as.character(word)), hjust=0.4, vjust=0, size = 8) + 
  geom_abline(slope=1, intercept = 0, color = "grey", linetype = "dotted", size = 5) +
  theme(legend.position="bottom") +
  geom_abline(slope=1, intercept = 0, color = "grey", linetype = "dotted") + 
  xlim(6.6, 7.2) +
  theme(strip.text.y = element_text(
        size = 10, color = "black"), 
        axis.text=element_text(size=10), 
        axis.title=element_text(size=10)) + 
  theme(legend.text = element_text(size = 36), 
        legend.title = element_text(size = 36),
        strip.text = element_text(
        size = 36, color = "black"),
        axis.text=element_text(size=36),
        strip.text.y = element_text(
        size = 36, color = "black"), 
        panel.spacing = unit(6, "lines"), 
        legend.spacing = unit(6.0,'cm'), 
        plot.margin = margin(1.5,1.5,1.5,1.5, "cm"),
        axis.title=element_text(size=36), legend.position = "bottom") 
g.response.time

ggsave("../plots/roar_cat_study1_figure4.png")
ggsave("../plots/roar_cat_study1_figure4.pdf")
```

## compare intercept, slop, and cor
```{r}
df.compare.difficulty <- data.frame(rbind(function.compare.params(df.params.ready, "Calibration", "A", "real"),
function.compare.params(df.params.ready, "Calibration", "A", "pseudo"),
function.compare.params(df.params.ready, "Calibration", "B", "real"),
function.compare.params(df.params.ready, "Calibration", "B", "pseudo"),
function.compare.params(df.params.ready, "Calibration", "C", "real"),
function.compare.params(df.params.ready, "Calibration", "C", "pseudo"))) 

colnames(df.compare.difficulty) <- c("group1", "group2","realpseudo", "correlation", "slope", "intercept")
```


```{r}
df.compare.rt <- data.frame(rbind(
function.compare.params(df.params.rt, "Calibration", "A", "real"),
function.compare.params(df.params.rt, "Calibration", "A", "pseudo"),
function.compare.params(df.params.rt, "Calibration", "B", "real"),
function.compare.params(df.params.rt, "Calibration", "B", "pseudo"),
function.compare.params(df.params.rt, "Calibration", "C", "real"),
function.compare.params(df.params.rt, "Calibration", "C", "pseudo"))) 

colnames(df.compare.rt) <- c("group1", "group2","realpseudo", "correlation", "slope", "intercept")
```

```{r}
df.compare <- df.compare.difficulty %>% 
  add_column(metric = "item difficulty") %>% 
  rbind(df.compare.rt %>% add_column(metric = "log response time"))
```

```{r fig.height = 3, fig.width=2.5}
g.item.difficulty / g.response.time
```

# Correlation Stats
```{r}
df.params.ready.real.only <- df.params.ready %>% 
  filter(realpseudo == "real")

df.params.ready.pseudo.only <- df.params.ready %>% 
  filter(realpseudo == "pseudo")
```

```{r}
cor.test(df.params.ready.real.only$Calibration, df.params.ready.real.only$A)
cor.test(df.params.ready.real.only$Calibration, df.params.ready.real.only$B)
cor.test(df.params.ready.real.only$Calibration, df.params.ready.real.only$C)
```

```{r}
cor.test(df.params.ready.pseudo.only$Calibration, df.params.ready.pseudo.only$A)
cor.test(df.params.ready.pseudo.only$Calibration, df.params.ready.pseudo.only$B)
cor.test(df.params.ready.pseudo.only$Calibration, df.params.ready.pseudo.only$C)
```
```{r}
result <- cor.test(df.params.ready.pseudo.only$Calibration, df.params.ready.pseudo.only$C)
result$
```

# Randomize group effect 
```{r message = FALSE, warning = FALSE, results='hide'}
rasch.model.params2 <- function (df, id) {
  df.response <- df %>% 
    filter(groupId == id) %>% 
    select(-c(groupId))
  
  r.m.g <- mirt(as.matrix(df.response), 1, itemtype = "Rasch", guess = 0.5, SE = TRUE, 
              technical = list(NCYCLES = 200))
  
  params <- data.frame(coef(r.m.g, IRTpars = TRUE, simplify = TRUE))$items.b
  
  params
}
```

```{r}
df.data2 <- df.data %>% 
  select(-c(correct.an, correct.rackle, correct.potent, correct.garment, correct.bads, correct.streat)) 
```


```{r message = FALSE, warning = FALSE, results='hide'}
list.corA <- NULL
list.corB <- NULL
list.corC <- NULL
list.corA.lower <- NULL
list.corB.lower <- NULL
list.corC.lower <- NULL
list.corA.higher <- NULL
list.corB.higher <- NULL
list.corC.higher <- NULL

for (i in 1:50){
  print(i)
  df.data.random.group.id <- df.data2 %>% 
  mutate(groupId = sample(sample(c("Calibration", "A", "B", "C"), length(df.data2$groupId), 
                                 prob = c(306/1960,1230/1960, 315/1960, 109/1960), replace = TRUE))) %>% 
  select(-c(pid, subGroup, ageMonths, grade, session))
  
  list <- df.data.random.group.id %>% 
    group_by(groupId) %>% 
    summarise(across(everything(), mean))  %>% 
    select(-groupId) %>% 
    as.matrix() %>% 
    as.numeric()
  
  if(!any(list >= 1)) {
    calibration <- rasch.model.params2(df.data.random.group.id,"Calibration")
    A <- rasch.model.params2(df.data.random.group.id,"A")
    B <- rasch.model.params2(df.data.random.group.id,"B")
    C <- rasch.model.params2(df.data.random.group.id,"C")
    
    cor.A <- cor.test(calibration, A)
    cor.B <- cor.test(calibration, B)
    cor.C <- cor.test(calibration, C)
  
  list.corA <- c(list.corA, as.numeric(cor.A$estimate))
  list.corB <- c(list.corB, as.numeric(cor.B$estimate))
  list.corC <- c(list.corC, as.numeric(cor.C$estimate))
  
  list.corA.lower <- c(list.corA.lower, as.numeric(cor.A$conf.int[1]))
  list.corA.higher <- c(list.corA.higher, as.numeric(cor.A$conf.int[2]))
  
  list.corB.lower <- c(list.corB.lower, as.numeric(cor.B$conf.int[1]))
  list.corB.higher <- c(list.corB.higher, as.numeric(cor.B$conf.int[2]))
  
  list.corC.lower <- c(list.corC.lower, as.numeric(cor.C$conf.int[1]))
  list.corC.higher <- c(list.corC.higher, as.numeric(cor.C$conf.int[2]))
  
  }
}
```


```{r}
mean(list.corA)
mean(list.corA.higher)
mean(list.corA.lower)
```
```{r}
mean(list.corB)
mean(list.corB.higher)
mean(list.corB.lower)
```
```{r}
mean(list.corC)
mean(list.corC.higher)
mean(list.corC.lower)
```