---
title: "ROAR-CAT convergent validity"
author: "Wanjing Anya Ma"
date:  "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
---

# Load Packages

Let's first load the packages that we need for this chapter.

```{r, message=FALSE, warning = FALSE, echo = FALSE}
library("knitr") # for rendering the RMarkdown file
library("tidyverse") # for data wrangling 
library(dplyr)
library('ggpubr')
library(ggplot2)
library(patchwork)

library(caTools)
library(ROCR) 
library(caret)
library("modelr")
library(pROC)
library(viridis)
library(gridExtra)
library(sjPlot)
library(mgcv)
library(ggcorrplot)
library(WRS2)
```

# Load Model
```{r}
load("../models/theta_brs_model_0.2.rda")
```

# Data
ROAR-SWR data
```{r, message = FALSE, warning = FALSE, echo = FALSE}
# all grade data
df.fastbridge_data.linked.clean <- read_csv("../data/school/study3_assessment_data.csv")

df.swr.trials.clean.validation.with.grade <- read_csv("../data/school/study3_roar_swr_trials_data.csv")
```


## Validation Data
Number of participants who participated ROAR-SWR
```{r}
df.swr.trials.clean.validation.with.grade %>% 
  group_by(gradelevel, pid) %>% 
  tally() %>% 
  group_by(gradelevel) %>% 
  tally()
```

```{r}
df.swr.trials.clean.validation.with.grade.unique <- df.swr.trials.clean.validation.with.grade %>% 
  filter(completed == TRUE, trialNumTotal == 100) %>% 
  group_by(pid, gradelevel) %>% 
  summarise(timeStarted = min(timeStarted)) 
df.swr.trials.clean.validation.with.grade.rt <- df.swr.trials.clean.validation.with.grade %>% 
  filter(completed == TRUE) %>% 
  group_by(pid, timeStarted) %>% 
  summarise(medianRT = median(rt))

df.swr.trials.clean.validation.final <- df.swr.trials.clean.validation.with.grade %>% 
  filter(completed == TRUE, trialNumTotal == 100) %>% 
  dplyr :: select(pid, gradelevel, thetaEstimate, thetaEstimate2, thetaSE, thetaSE2, timeStarted) %>% 
  right_join(df.swr.trials.clean.validation.with.grade.unique, by = c("pid", "timeStarted", "gradelevel")) %>% 
  unique() %>% 
  inner_join(df.swr.trials.clean.validation.with.grade.rt, by = c("pid", "timeStarted")) %>% 
  dplyr :: select(pid, gradelevel, thetaEstimate,thetaEstimate2, thetaSE, thetaSE2, medianRT, timeStarted) %>% 
  filter(!is.na(gradelevel))

```

```{r}
df.clean.trials <- df.swr.trials.clean.validation.with.grade %>% 
  filter(completed == TRUE) %>% 
  left_join(df.swr.trials.clean.validation.final %>% select(pid, timeStarted) %>% add_column(keep = 1) ) %>% 
  filter(!is.na(keep)) %>% 
  unique()
```

## remove guessing

```{r}
df.data.rt.transformed <- df.clean.trials %>% 
  mutate(rt = ifelse(rt == 0, 0.01, rt)) %>% 
  mutate(log_rt = log(rt)) %>% 
  group_by(pid, runId,  block) %>% 
  summarise(median_log_rt = median(log_rt), median_rt = median(rt), pc = mean(correct)) 

mean_value <- mean(df.data.rt.transformed$median_log_rt)
sd_value <- sd(df.data.rt.transformed$median_log_rt)

threshold <- mean_value - 3*sd_value

print(threshold)

df.clean.trials.v2 <- df.data.rt.transformed %>% 
  filter(median_log_rt >= threshold) %>%
  ungroup() %>% 
  left_join(df.clean.trials)
```
additional filter


We keep particiapnts who doesn't have any block has median response time lower than 2 standard deviation
```{r}
df.included.names <- df.clean.trials.v2 %>% 
  group_by(pid) %>% 
  tally() %>% 
  filter(n > 50)

df.clean.trials.v3 <- df.clean.trials.v2 %>% 
  filter(pid %in% df.included.names$pid)
```


```{r}
df.excluded.participants <- df.clean.trials %>% 
  filter(!pid %in% df.included.names$pid) %>% 
  group_by(pid, block) %>% 
  mutate(block = as.character(block + 1)) %>% 
  summarise(pc = mean(correct), 
            median_rt = median(rt), 
            median_log_rt = median(log(rt))) %>% 
  mutate(guessing = ifelse(median_log_rt < threshold, TRUE, FALSE)) 

ggplot(df.excluded.participants, mapping = aes(x = block,
                     y = median_rt)) +
  geom_point(alpha=.6, aes(color = guessing)) +
  geom_line(aes(group=pid), alpha=.4) + 
  scale_color_manual(values=c( "black", "darkred")) + 
  labs(x = "block number",
       y = "median response time per item (ms)",
       title = "rapid-guessing particiapnts")
  
```



```{r}
df.swr.trials.clean.validation.final.v2 <- df.swr.trials.clean.validation.final %>% 
  filter(!pid %in% df.excluded.participants$pid)
```

```{r}
#X2022.2023.FAST.CBM.R.English.Window.2.Risk.Level"
df.FastBridge.risk <- df.fastbridge_data.linked.clean %>% 
  dplyr :: select(pid, FastBridge.risk = "X2022.2023.FAST.CBM.R.English.Window.2.Risk.Level") %>% 
  filter(!is.na(FastBridge.risk)) %>% 
  mutate(FastBridge.risk = ifelse(FastBridge.risk == "Ex", 0, 1))
```

```{r}
df.analysis.combine <- df.fastbridge_data.linked.clean %>% 
  dplyr :: select(pid, gradelevel,  `X2022.2023.FAST.Early.Reading.Window2.CBMR.English.Words.Read.Correct`,
         `Reading.F.P.GrK8.March.22.23.Independent.Reading.Level..A.Z.`) %>%
  dplyr::rename(FastBridge = `X2022.2023.FAST.Early.Reading.Window2.CBMR.English.Words.Read.Correct`,
                 F.P.March = `Reading.F.P.GrK8.March.22.23.Independent.Reading.Level..A.Z.`) %>%
  mutate(fp_score_march = tolower(F.P.March)) %>%
  mutate(fp_score_march = ifelse(fp_score_march == "below a", "a", fp_score_march)) %>%
  mutate(F.P.March = match(tolower(fp_score_march), letters)) %>%
  dplyr :: select(-fp_score_march) %>% 
  mutate(F.P.risk = if_else(((F.P.March < 7) & (gradelevel == 1))|((F.P.March < 11) & (gradelevel == 2)), 1, 0)) %>% 
  unique() %>% 
  inner_join(df.swr.trials.clean.validation.final.v2, by = c("pid", "gradelevel")) %>% 
  filter(medianRT >= 500) %>% 
  mutate(log_median_rt = log(medianRT), grade = paste("grade", gradelevel, " ")) 

```

With both swr and f.p
```{r}
df.analysis.combine %>% 
  filter(!is.na(F.P.March), !is.na(thetaEstimate)) %>% 
  group_by(gradelevel) %>% 
  tally() 
```

With both swr and FastBridge

```{r}
df.analysis.combine %>% 
  filter(!is.na(FastBridge), !is.na(thetaEstimate)) %>% 
  group_by(gradelevel) %>% 
  tally() 
```
With both F&P and FastBridge
```{r}
df.analysis.combine %>% 
  filter(!is.na(F.P.March), !is.na(FastBridge)) %>% 
  group_by(gradelevel) %>% 
  tally() 
```



# Correlation Matrices

```{r}
g.1 <- df.analysis.combine %>% filter(gradelevel == 1)

fastbrdige.g.1.pbcor <- pbcor(g.1$thetaEstimate, g.1$FastBridge)
f.p.g1.pbcor <- pbcor(g.1$thetaEstimate, g.1$F.P.March)

g.2 <- df.analysis.combine %>% filter(gradelevel == 2)
fastbrdige.g.2.pbcor <- pbcor(g.2$thetaEstimate, g.2$FastBridge)
f.p.g2.pbcor <- pbcor(g.2$thetaEstimate, g.2$F.P.March)

fastbrdige.g.1.pbcor 
fastbrdige.g.2.pbcor 
f.p.g1.pbcor
f.p.g2.pbcor
```

```{r}
df.analysis.combine.longer <- df.analysis.combine %>% 
  pivot_longer(cols = c("FastBridge", "F.P.March"), names_to = "assessments", 
               values_to = "score")

```

```{r}
df.analysis.combine %>% filter(!is.na(FastBridge)) %>% 
  arrange(thetaEstimate)
```


```{r fig.width=3,fig.height=3}
g.1.fb <- ggplot(df.analysis.combine %>% filter(!is.na(FastBridge), gradelevel == 1),
       aes(x = thetaEstimate,
           y = FastBridge, color = log_median_rt)) +
  #facet_wrap(~grade) +
  geom_point(size = 3) +
  labs(x = "ROAR-CAT", 
       y = "FastBridge Early Reading",
       title = "Grade 1") + 
  annotate("text", x = -5, y = 200, label = paste0("r = ", round(fastbrdige.g.1.pbcor$cor, digits = 2))) +
  geom_smooth(method = MASS::rlm, color="black", size = 2) +
  scale_color_viridis(option = 'plasma') + 
  theme(legend.position = "none") + 
  ylim(0, 250) + 
  xlim(-6, 6)

g.2.fb <- ggplot(df.analysis.combine %>% filter(!is.na(FastBridge), gradelevel == 2),
       aes(x = thetaEstimate,
           y = FastBridge, color = log_median_rt)) +
  #facet_wrap(~grade) +
  geom_point(size = 3) +
  labs(x = "ROAR-CAT", 
       y = "FastBridge Early Reading",
       title = "Grade 2") + 
  annotate("text", x = -5, y = 200, label = paste0("r = ", round(fastbrdige.g.2.pbcor$cor, digits = 2))) +
  geom_smooth(method = MASS::rlm, color="black", size = 2) +
  scale_color_viridis(option = 'plasma') + 
  theme(legend.position = "none") + 
  ylim(0, 250) + 
  xlim(-6, 6)


g.1.fp <- ggplot(df.analysis.combine %>% filter(!is.na(F.P.March), gradelevel == 1),
       aes(x = thetaEstimate,
           y = F.P.March, color = log_median_rt)) +
  geom_point(size = 3) +
  geom_smooth(method = MASS::rlm, color="black", size = 2) +
  scale_color_viridis(option = 'plasma') +
  labs(x = "ROAR-CAT",
       y = "Fountas & Pinnell",
       title = "Grade 1",
       color = "median response time (log ms)") +
  annotate("text", x = -5, y = 12, label = paste0("r = ", round(f.p.g1.pbcor$cor, digits = 2))) +
 # stat_cor(method = "pearson", cor.coef.name = 'r', aes(label = ..r.label..), size = 10) +
  scale_y_continuous(breaks = c(2,5,8,11,14,17),labels=c('B','E','H','K','N',"Q")) + 
  theme(legend.position = "none")

g.2.fp <- ggplot(df.analysis.combine %>% filter(!is.na(F.P.March), gradelevel == 2),
       aes(x = thetaEstimate,
           y = F.P.March, color = log_median_rt)) +
  geom_point(size = 3) +
  geom_smooth(method = MASS::rlm, color="black", size = 2) +
  scale_color_viridis(option = 'plasma') +
  labs(x = "ROAR-CAT",
       y = "Fountas & Pinnell",
       title = "Grade 2",
       color = "median response time (log ms)") +
  annotate("text", x = -5, y = 12, label = paste0("r = ", round(f.p.g2.pbcor$cor, digits = 2))) +
 # stat_cor(method = "pearson", cor.coef.name = 'r', aes(label = ..r.label..), size = 10) +
  scale_y_continuous(breaks = c(2,5,8,11,14,17),labels=c('B','E','H','K','N',"Q")) +
  theme(legend.position = "bottom")
((g.1.fb + g.2.fb) / (g.1.fp + g.2.fp)) + 
  theme(strip.text = element_text(
        size = 36, color = "black"),
        title = element_text(
        size = 36, color = "black"), 
        legend.text = element_text(size = 24), 
        legend.title = element_text(size = 24),
        axis.text=element_text(size=36),
        plot.margin = margin(1.5,1.5,1.5,1.5, "cm"),
        panel.spacing = unit(1, "lines"), 
        panel.grid = element_line(size = 2), 
        axis.title=element_text(size=36), legend.position = "none")

ggsave("../plots/roar_cat_study3_figure1.png")
ggsave("../plots/roar_cat_study3_figure1.pdf")
#ggsave("../plots/convergent_validity.png", g.1/g.2, width = 8, height = 8)
```


# Check correlation by number of test items

```{r}
df.trials.combined <- df.clean.trials.v3 %>% 
  filter(corpusId != "corpusNew") %>% 
  dplyr::select(pid, runId, trialNumTotal,thetaEstimate, thetaSE) %>% 
  left_join(df.analysis.combine %>% dplyr :: select(-c(thetaEstimate)), by = c("pid")) %>% 
  #filter(medianRT >= 397) %>% 
  left_join(df.FastBridge.risk, by = "pid") %>% 
  unique()
```

```{r}
df.trials.combined.delete.new <- df.trials.combined %>% 
  left_join(df.trials.combined %>% 
  group_by(trialNumTotal) %>% 
  tally() %>% 
  add_column(trialNumTotal.new = seq(1, 84, 1)) %>% 
  select(-n))
```

```{r}
df.fastbridge.cor.curve <- df.trials.combined.delete.new %>% 
  filter(!is.na(FastBridge)) %>% 
  group_by(gradelevel, trialNumTotal.new) %>% 
  summarise(correlation = WRS2 :: pbcor(thetaEstimate, FastBridge, alpha = 0.05)$cor) %>% 
  mutate(grade = as.character(gradelevel))

g.c.1 <- ggplot(df.fastbridge.cor.curve, mapping = aes(x = trialNumTotal.new,
                     y = correlation)) +
  geom_smooth(se = FALSE, color = "black", aes(linetype = grade)) +
  labs(x = "Number of ROAR-CAT items",
       y = "Correlation", 
       title = "FastBrdige vs. ROAR-CAT") + 
  scale_y_continuous(limits = c(0.3, 1), breaks = round(seq(0, 1, by = 0.1),1)) + 
  theme(legend.position = "none") + 
  scale_color_manual(values=c("black", "grey30"))

df.FP.cor.curve <- df.trials.combined.delete.new %>%
  filter(!is.na(F.P.March)) %>%
  group_by(gradelevel, trialNumTotal.new) %>%
  summarise(correlation = WRS2 :: pbcor(thetaEstimate, F.P.March)$cor) %>%
  mutate(grade = as.character(gradelevel))

g.c.2 <-ggplot(df.FP.cor.curve, mapping = aes(x = trialNumTotal.new,
                     y = correlation)) +
  geom_smooth(se = FALSE, color = "black", aes(linetype = grade)) +
  labs(x = "Number of ROAR-CAT items",
       y = "Correlation", 
       title = "F.P vs. ROAR-CAT") + 
  scale_y_continuous(limits = c(0.3, 1), breaks = round(seq(0, 1, by = 0.1),1)) + 
  scale_color_manual(values=c("black", "grey30")) + 
  theme(legend.position = "bottom") 

g.c.1 + g.c.2
```


# Check time spent
```{r}
df.FP.cor.curve <- df.clean.trials.v3 %>% 
  filter(trialNumTotal == 1) %>% 
  select(pid, runId,  time_elapsed, gradelevel) %>% 
  dplyr :: rename(init_elapsed = time_elapsed) %>% 
  right_join(df.clean.trials.v3) %>% 
  filter(!is.na(init_elapsed)) %>% 
  mutate(time_diff = abs(time_elapsed-init_elapsed)) %>%
  select(pid, runId,  trialNumTotal, time_diff, thetaEstimate, gradelevel) %>% 
  left_join(df.analysis.combine %>% select(pid, F.P.March, FastBridge), by = c("pid")) %>% 
  group_by(trialNumTotal, gradelevel) %>% 
  filter(!is.na(F.P.March)) %>% 
  summarise(correlation = WRS2 :: pbcor(thetaEstimate, F.P.March, alpha = 0.05)$cor, time = mean(time_diff)/1000) %>%
  mutate(grade = as.character(gradelevel))

df.FastBridge.cor.curve <- df.clean.trials.v3 %>% 
  filter(trialNumTotal == 1) %>% 
  select(pid, runId,  time_elapsed, gradelevel) %>% 
  dplyr :: rename(init_elapsed = time_elapsed) %>% 
  right_join(df.clean.trials.v3) %>% 
   filter(!is.na(init_elapsed)) %>% 
  mutate(time_diff = abs(time_elapsed-init_elapsed)) %>%
  select(pid, runId,  trialNumTotal, time_diff, thetaEstimate, gradelevel) %>% 
  left_join(df.analysis.combine %>% select( pid, F.P.March, FastBridge), by = c("pid")) %>% 
  group_by(trialNumTotal, gradelevel) %>% 
  filter(!is.na(FastBridge)) %>% 
  summarise(correlation = WRS2 :: pbcor(thetaEstimate, FastBridge, alpha = 0.05)$cor, time = mean(time_diff)/1000) %>%
  mutate(grade = as.character(gradelevel))
```

```{r}
g.c.1 <- ggplot(df.FastBridge.cor.curve, mapping = aes(x = time,y = correlation)) +
  geom_smooth(se = FALSE, color = "black", aes(linetype = grade)) +
  labs(x = "Test length (second)",
       y = "Correlation", 
       title = "FastBrdige vs. ROAR-CAT") + 
  scale_y_continuous(limits = c(0.3, 1), breaks = round(seq(0, 1, by = 0.1),1)) +
  scale_x_continuous(limits = c(0, 360), breaks = round(seq(0, 360, by = 60),1)) +
  theme(legend.position = "none") + 
  scale_color_manual(values=c("black", "grey30"))

g.c.2 <- ggplot(df.FP.cor.curve, mapping = aes(x = time,
                     y = correlation)) +
  geom_smooth(se = FALSE, color = "black", aes(linetype = grade)) +
  labs(x = "Test length (second)",
       y = "Correlation", 
       title = "F.P and ROAR-CAT") + 
  scale_y_continuous(limits = c(0.3, 1), breaks = round(seq(0, 1, by = 0.1),1)) +
  scale_x_continuous(limits = c(0, 360), breaks = round(seq(0, 360, by = 60),1)) +
  scale_color_manual(values=c("black", "grey30")) + 
  theme(legend.position = "right") 

g.c.1 + g.c.2

ggsave("../plots/roar_cat_study3_figure2.png")
ggsave("../plots/roar_cat_study3_figure2.pdf")
```



